Deterministic Scheduling of Periodic Messages in a Network

### 2017-07-19 infocom/infocom.tex
mkdir infocom

\documentclass[a4paper,10pt]{article}
%\documentclass[10pt, conference, letterpaper]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{url}
\usepackage{graphicx,graphics} 
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{complexity}
\usepackage{tkz-graph}
\usepackage{float}
\usepackage{setspace}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{authblk}
% \usepackage{hyperref}

@@

\author[1]{Ma\"el Guiraud}
\author[1]{Dominique Barth}
% \author[1]{Christian Cad\'er\'e}
\author[2]{Brice Leclerc}
\author[2]{Olivier Marc\'e}
\author[1]{Yann Strozecki}
\affil[1]{David Laboratory, UVSQ}
\affil[2]{Nokia Bell Labs France}

@@

\footnote{This work is partially supported by the french ANR project N-GREEN.}

@@

      \begin{figure}[ht]
      \begin{center}
          \scalebox{0.8}{

@@

      \begin{center}
      \includegraphics[width=\textwidth]{rrh.pdf}
      \end{center}

@@

       \begin{center}
      \includegraphics[width=\textwidth]{BBU.pdf}
      \end{center}

@@

      The following table summarize the main notations used in the paper.
      \begin{center}
   \begin{tabular}{|c|c|}
    \hline
     $(G,\cal R)$ & Routed network \\
     \hline
      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
      \hline
      $\lambda(u_i,r)$ & Latency of the vertex $u_i$ in $r$\\
         \hline
         $\lambda(r)$ & Length of the route $r$\\
         \hline
         $P$ & Period\\
         \hline
         $\tau$ & Size of a message\\
         \hline
         $ [t(v,r)]$& Set of time slots used by route $r$ at vertex $v$ \\
         & in a period $P$\\
         \hline 
         ${\cal M}=(m_0, \ldots ,m_{n-1})$& Assignment: an offset for each route)\\
              \hline 
         $w_r$& Waiting time of the route $r$\\
            \hline 
         $PT(r)$& Process time of the route $r$\\
           \hline 
         $MT({\cal M})$& Maximum process time of the assignment\\
    \hline

      \end{tabular}
      \end{center}

@@

    \scalebox{0.5}{
    \begin{tikzpicture}
    \tikzset{
      LabelStyle/.style = { rectangle, rounded corners, draw,
			  font = \bfseries },
      EdgeStyle/.append style = {->} }
      \SetGraphUnit{5}

@@

      \begin{center}
      \includegraphics[width=\textwidth]{ex3nt.png}
      \end{center}
% 	\begin{algorithm}[H]
% 	\caption{Greedy assignment}
% 	\begin{algorithmic}
% 	\REQUIRE ${\cal R}_{\cal C}$, period $P$
% 	\ENSURE A P-periodic assignment in p $\leq P$, or FAILURE
% 	\STATE $T$ a table of the macro slots of size $\tau$ in the forward period.
% 	\STATE $L$ a list of free intervals in the backward period%$P2[P]$ slots backward period.
% 	\FORALL{source $s$ in S}
% 
% 	\FORALL{free intervals $[a,b]$ in $L$}
% 	\FORALL{ $a/\tau - \lambda(s) <j< b/\tau - \lambda(s)$ }
% 	\IF{ $T[j] == FREE$}
% 	\STATE $m_{s} \leftarrow j.\tau$
% 	\STATE $T[j] = USED$
% 	\STATE update $[a,b]$ in $L$
% 	\STATE BREAK
% 	\ENDIF
% 	\ENDFOR
% 	\ENDFOR
% % 	
% % 	\IF{No intervals are found for $s_i$}
% % 	\STATE return FAILURE
% % 	\ENDIF
% % 	\ENDFOR
% 
% 	\ENDFOR
% 
% 	\end{algorithmic}
% 	\end{algorithm}

@@

      \begin{center}
	\includegraphics[scale=0.4]{periode_petite.pdf}
      \end{center}
      \caption{Minimum period averaged over $1000$ random instances}
      \end{figure}

@@

       \begin{center}
      \includegraphics[scale=0.4]{echec_longues.pdf}
      \end{center}
      \caption{Success rate for $8$ routes over $1000$ random instances}
     \end{figure}

@@

      Since the exhaustive search solve PAZL in an FPT time, with parameter $n$ the number of routes, we study the scalability of the time needed by this algorithm, according to $n$. We made an experiment on $100$ random star routed networks, in which the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots. We fixed the period to $n\tau+1000$, that corresponds to loads of $\simeq 70\%$ (for $1$ route) to $\simeq 98\%$ (for 21 routes).
         \begin{center}
         \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Number of routes & $1$ & $6$ & $11$& $16$& $21$\\
    \hline
    Average time before answer (ms) & $0.004$ &$0.027$&$0.599$&$59.711$&$14866.1$\\
    \hline
      \end{tabular}
      \end{center}

@@

\begin{figure}[H] 
    \begin{minipage}[c]{6cm}
  \centering
      \includegraphics[width=6cm]{departs_gp_21000.pdf}

      \caption{Success rate of different orders, $95\%$ load.}
      \end{minipage} \hfill
        \begin{minipage}[c]{6cm}
          \includegraphics[width=6cm]{departs_gp_25000.pdf}
      \caption{Success rate of different orders, $80\%$ load.}

>>>>

%\documentclass[a4paper,10pt]{article}
\documentclass[10pt, conference, letterpaper]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{url}
\usepackage{graphicx,graphics} 
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{complexity}
\usepackage{tkz-graph}
\usepackage{float}
\usepackage{tabularx}
\usepackage{setspace}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{authblk}
% \usepackage{hyperref}

@@

%\author[1]{Ma\"el Guiraud}
%\author[1]{Dominique Barth}
% \author[1]{Christian Cad\'er\'e}
%\author[2]{Brice Leclerc}
%\author[2]{Olivier Marc\'e}
%\author[1]{Yann Strozecki}
%\affil[1]{David Laboratory, UVSQ}
%\affil[2]{Nokia Bell Labs France}

@@

%\footnote{This work is partially supported by the french ANR project N-GREEN.}

@@

      \begin{figure}[ht]
      \begin{center}
          \scalebox{0.5}{

@@

      \begin{center}
     \hspace{-0.5cm} \includegraphics[width=0.48\textwidth]{rrh.pdf}
      \end{center}

@@

       \begin{center}
     \hspace{-0.5cm} \includegraphics[width=0.48\textwidth]{BBU.pdf}
      \end{center}

@@

%      The following table summarize the main notations used in the paper.
%      \begin{center}
%   \begin{tabular}{|c|c|}
%    \hline
%     $(G,\cal R)$ & Routed network \\
%     \hline
%      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
%      \hline
%      $\lambda(u_i,r)$ & Latency of the vertex $u_i$ in $r$\\
%         \hline
%         $\lambda(r)$ & Length of the route $r$\\
%         \hline
%         $P$ & Period\\
%         \hline
%         $\tau$ & Size of a message\\
%         \hline
%         $ [t(v,r)]$& Set of time slots used by route $r$ at vertex $v$ \\
%         & in a period $P$\\
%         \hline 
%         ${\cal M}=(m_0, \ldots ,m_{n-1})$& Assignment: an offset for each route)\\
%              \hline 
%         $w_r$& Waiting time of the route $r$\\
%            \hline 
%         $PT(r)$& Process time of the route $r$\\
%           \hline 
%         $MT({\cal M})$& Maximum process time of the assignment\\
%    \hline
%
%      \end{tabular}
%      \end{center}

@@

    \hspace{0.5cm}\scalebox{0.35}{
    \begin{tikzpicture}
    \tikzset{
      LabelStyle/.style = { rectangle, rounded corners, draw,
			  font = \bfseries },
      EdgeStyle/.append style = {->} }
      \SetGraphUnit{5}

@@

      \begin{center}
      \includegraphics[width=0.48\textwidth]{ex3nt.png}
      \end{center}
% 	\begin{algorithm}[H]
% 	\caption{Greedy assignment}
% 	\begin{algorithmic}
% 	\REQUIRE ${\cal R}_{\cal C}$, period $P$
% 	\ENSURE A P-periodic assignment in p $\leq P$, or FAILURE
% 	\STATE $T$ a table of the macro slots of size $\tau$ in the forward period.
% 	\STATE $L$ a list of free intervals in the backward period%$P2[P]$ slots backward period.
% 	\FORALL{source $s$ in S}
% 
% 	\FORALL{free intervals $[a,b]$ in $L$}
% 	\FORALL{ $a/\tau - \lambda(s) <j< b/\tau - \lambda(s)$ }
% 	\IF{ $T[j] == FREE$}
% 	\STATE $m_{s} \leftarrow j.\tau$
% 	\STATE $T[j] = USED$
% 	\STATE update $[a,b]$ in $L$
% 	\STATE BREAK
% 	\ENDIF
% 	\ENDFOR
% 	\ENDFOR
% % 	
% % 	\IF{No intervals are found for $s_i$}
% % 	\STATE return FAILURE
% % 	\ENDIF
% % 	\ENDFOR
% 
% 	\ENDFOR
% 
% 	\end{algorithmic}
% 	\end{algorithm}

@@

      \begin{center}
	\includegraphics[width=0.5\textwidth]{periode_petite.pdf}
      \end{center}
      \caption{Minimum period averaged over $1000$ random instances}
      \end{figure}

@@

       \begin{center}
      \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{echec_longues.pdf}
      \end{center}
      \caption{Success rate for $8$ routes over $1000$ random instances}
     \end{figure}

@@

      Since the exhaustive search solve PAZL in an FPT time, with parameter $n$ the number of routes, we study the scalability of the time needed by this algorithm, according to $n$. In the following experiment, the weights of the arcs $(c_t,t_i)$ are drawn following an uniform distribution between $0$ and $30000$ slots. We fixed the period to $n\tau+1000$, that corresponds to loads of $\simeq 70\%$ (for $1$ route) to $\simeq 98\%$ (for 21 routes).
      The following table shows the average time before the exhaustive search ends, for $1$ to $21$ routes. Theses results are computed on $100$ random star routed networks.
         \begin{center}
         \begin{tabularx}{0.5\textwidth}{|X|X|X|X|X|X|}
    \hline
   $n$ & $1$ & $6$ & $11$& $16$& $21$\\
    \hline
   Time (ms) & $0.004$ &$0.027$&$0.599$&$59.711$&$14866.1$\\
    \hline
      \end{tabularx}
      \end{center}

@@

\begin{figure}[H] 
    \begin{minipage}[c]{0.5\textwidth}
  \centering
      \includegraphics[width=0.5\textwidth]{departs_gp_21000.pdf}

      \caption{Success rate of different orders, $95\%$ load.}
      \end{minipage} \hfill
        \begin{minipage}[c]{0.5\textwidth}
          \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
      \caption{Success rate of different orders, $80\%$ load.}
